The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-08-13 paper/mri paper.tex
matrices

We define the flux function $\mathbf{A}$ and streamfunction $\mathbf{\Psi}$. These are scalar fields defined as the curl of the magnetic field and velocity, respectively, and so automatically satisfy our constraints.

$\mathbf{A}$ is thus related to the magnetic field as

@@

>>>>

We define the flux function $A$ and streamfunction $\Psi$. These are scalar fields defined as the curl of the magnetic field and velocity, respectively, and so automatically satisfy our constraints.

$A$ is thus related to the magnetic field as

@@

The destabilizing substitution is made, and Equations \ref{eqset1} - \ref{eqset4} are rewritten such that the fluid variables are contained in a state vector $\mathbf{V} = \left[\Psi, u_y, A, B\right]^\mathrm{T}$. This yields the following system of equations.

\beq
\mathcal{D}\partial_t \mathbf{V} + \mathbf{N} = \mathcal{L} \mathbf{V} - \epsilon^2\partial_z\mathcal{X} \mathbf{V} - \epsilon^2 \partial_z^3 \mathcal{L}_3\mathbf{V}
\eeq

Where $\mathcal{L} \equiv \mathcal{L}_0 + \mathcal{L}_1\partial_z + \mathcal{L}_2\partial_z^2 + \mathcal{L}_3\partial_z^3 + \mathcal{L}_4\partial_z^4$ \\

And: \\

$\mathcal{D} = \left[\begin{matrix}
\nabla^2 & 0 & 0 & 0 \\
0 & 1& 0 & 0 \\
0 & 0 & 1 & 0\\
0 & 0 & 0 & 1 \\
\end{matrix}\right]$ \\

$\mathcal{L}_0 = \left[\begin{matrix}
\frac{1}{\reye}\partial_x^4 & 0 & 0 & 0 \\
0 & \frac{1}{\reye}\partial_x^2 & 0 &0 \\
0 & 0 & \frac{1}{\reym}\partial_x^2 & 0 \\
0 & 0 & 0 & \frac{1}{\reym}\partial_x^2 \\ \end{matrix}\right] $ \\

\vspace{2mm}

$\mathcal{L}_1 = \left[\begin{matrix}
0 & 2 & \frac{2}{\beta}\partial_x^2 & 0 \\
(\Omega_0 - 2)q & 0 & 0 & \frac{2}{\beta} \\
1 & 0 & 0 & 0 \\
0 & 1 & -q\Omega_0 & 0 \\ \end{matrix}\right] \\$

\vspace{2mm}

$\mathcal{L}_2 = \left[\begin{matrix}
2\frac{1}{\reye} \partial_x^2 & 0 & 0 & 0 \\
0 & \frac{1}{\reye} & 0 & 0 \\
0 & 0 & \frac{1}{\reym} & 0 \\
0 & 0 & 0 & \frac{1}{\reym} \\ \end{matrix}\right]$

\vspace{2mm}

$\mathcal{L}_3 = \left[\begin{matrix}
0 & 0 & \frac{2}{\beta} & 0 \\
0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 \\ \end{matrix} \right] $

\vspace{2mm}

$\mathcal{L}_4 = \left[\begin{matrix}
\frac{1}{\reye} & 0 & 0 & 0 \\
0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 \\ \end{matrix}\right] $ \\

\vspace{2mm}

$\mathcal{X} = \left[\begin{matrix}
0 & 0 & \frac{2}{\beta}\partial_x^2 & 0 \\
0 & 0 & 0 & \frac{2}{\beta} \\
1 & 0 & 0 & 0 \\
0 & 1 & 0 & 0 \\ \end{matrix} \right].$ \\
